Adopting agile in the large: motivations, success factors and challenges

### 2013-11-05 journal/article.tex
Fulltext filtering
Filtering and notes on inclusion criteria

@@

>>>>

--> Case ``only piloting'': Piloting cases that clearly span only one limited
    project are excluded. Especially if there is no discussion of the continuity
    of agile. See Scott 2008.

--> Cases must be empirical, i.e. present a real case. (Otherwise we would need
    to include textbooks also...)

@@

--> The company must already be with N teams or N people, not growing up to the
    required numbers. Small companies in growth are therefore excluded.
